Observation of the orientation of snow hydrometeors at sheltered and unsheltered sites

### 2024-12-11 Review_R1_answers_202412.tex

\subsubsection*{Major comments:}
\begin{enumerate}
    \item \textit{The discussion about the impact of the environmental winds on the orientation of the snowflakes is not sound. Wind speed alone may not be sufficient to capture this impact. The distribution of wind components likely plays a more significant role.}

    We agree with the reviewer that the distribution of wind components and turbulence at the relevant scales is probably more important than simple wind speed that we could investigate in this work (as all the MASC measurements in the database have wind speed information).

    We carefully revised the manuscript to make sure not to overstate the role of wind speed alone and also to clarify when we cannot separate between the "natural" contribution of wind on the distribution of orientations and the "artificial" contribution due to the turbulence generated by strong wind interacting with the hollow measurement system of the MASC. A few changes are highlighted in the manuscript, we can cite for example in Sec.~3:

    \blue{Atmospheric conditions are expected to play a role in shaping orientation distributions: atmospheric turbulence is probably a key driver, as well as horizontal winds interacting with the instrument frame~\cite{Fitch_AMT_2021}. Turbulence has been shown to heavily impact the falling of particles in fluids in general~\cite{Petersen_JFM_2019,Brandt_ARFM_2022} and of frozen hydrometeors in particular~\cite{Nemes_JFM_2017,Li_JFM_2021}.}

@@

\subsubsection*{Comments:}

\begin{enumerate}

    \item \textit{There is a very recent laboratory study about ice particle orientation which should be added to reference list and I also highly suggest to discuss their results. They appear to be slightly contradictory to your study:} \cite{Stout_ACP_2024} \\

    We thank the reviewer for this, extremely relevant, recommendation.  This high quality study, with laboratory experiments using snowflake replicas in a liquid solution shows that planar crystals may be falling with regimes that do not have a preferential orientation around 0$^\circ$. We believe that, given some of the assumptions of~\cite{Stout_ACP_2024}, their results are somehow complementary to our work and point out to the need to better understand the role of turbulence in orientation of snow particles. Regarding the cited study, we have the following comments:
    \begin{itemize}
        \item A relevant limitation of this work is that "it  only considers quiescent conditions, as the authors want to know under what conditions particle instability still occurs, even without the addition of turbulence.". This is quite different with respect to our field-based experiments.
        \item The study focuses on planar crystals and it uses 12 sub-types of this  hydrometeors (from plates to dendrites). In our case, the planar crystals are all classified together into an individual class, which is also one of the most difficult to classify with the MASC and to observe (given the 35 microns resolution of the MASC itself). In this sense our study is coarser and cannot go to this level of detail, which could be a reason why we do not observe such behavior. 
        \item Interestingly, another recent study~\cite{Koebschall_EF_2023} using replicas of snow aggregates and a liquid solution, showed instead that the particles tend to orient such that the area projected in the direction of flow is maximized, which is the type of behavior that is consistent with our observations. This is very interesting as two separate indoor studies, with similar methods, seem to indicate that individual crystals of planar type and aggregate snowflakes may be behaving differently regarding preferential orientation.
        \item It is unfortunate that the study reports, as possible backup evidence and as driving motivation, that previous studies using MASC also showed off-zero preferential orientations. This is exactly what we showed, in our paper, to be due to the bias of averaging \textbf{absolute value} of orientation estimates taken from different viewpoints and it was one of the driving motivation of our publication.  
        \item A further limitation is that the study considers objects falling in a liquid, which implies a far lower density ratio compared to hydrometeors in air, which in turn can impact the settling dynamics as discussed in recent studies by one of our coauthors (see~\cite{Tinklenberg_JFM_2023,Tinklenberg_JFM_2024}).
    \end{itemize}

    We now modified the manuscript to give some space to commenting and elaborating on the findings of~\cite{Stout_ACP_2024}. At first, we include this study in Table~1. Then, in the Introduction, we mention this study as:\\
    \blue{ A recent laboratory study using snow crystals replicas falling in an alcoholic solution~\cite{Stout_ACP_2024}, however, shows that in quiescent conditions individual planar crystals may have a spiralling fall regime with preferential orientations that depart from 0$^\circ$. A study with similar methods, but focussing on larger snow aggregates showed instead that horizontal orientation is preferred for those hydrometeors~\cite{Koebschall_EF_2023}. It is to be remarked that those and other studies, in considering objects falling in liquids, use a solid-to-fluid density ratio which is orders lower than in atmospheric precipitation. This may have far-reaching consequences in the settling dynamics~\cite{Tinklenberg_JFM_2023,Tinklenberg_JFM_2024}.  }\\

### 2024-12-11 Grazioli_JGRA_2024_R1.tex
Updates from Overleaf

Considering a population of hydrometeors rather than individual particles, as is often the case for practical applications, the distribution of orientations is often modeled with relatively narrow variability around 0$^\circ$ (i.e., horizontally oriented) values. Looking at the overview in Table~\ref{table:orientations}, one can observe that modeling studies mostly assume a Gaussian distribution, with standard deviations varying between 3$^\circ$ \cite{Matrosov_JAM_2001} and 60$^\circ$ \cite{Putnam_MWR_2017} depending on the type of hydrometeors. Observational studies conducted in the field \cite{Garrett_GRL_2015} confirm that differences exist due to hydrometeor type and environmental conditions (wind and turbulence). They report as well non-zero mean and median orientation values, which is contradictory with what was stated previously. As we will discuss later in this study, this discrepancy can be the result of the way multi-view instrumental observations are combined to retrieve an overall estimate of orientation, at least for more complex three-dimensional snow particles. A recent laboratory study using snow crystals replicas falling in an alcoholic solution~\cite{Stout_ACP_2024}, however, shows that in quiescent conditions individual planar crystals may have a spiralling fall regime with preferential orientations that depart from 0$^\circ$. A study with similar methods, but focussing on larger snow aggregates showed instead that horizontal orientation is preferred for those hydrometeors~\cite{Koebschall_EF_2023}.

@@

Atmospheric conditions are expected to play a role in shaping orientation distributions: atmospheric turbulence is probably a key driver, as well as horizontal winds interacting with the instrument frame~\cite{Fitch_AMT_2021}. Figure~\ref{fig:wind-effect} compares the standard deviation of orientation distributions between DFIR and unsheltered sites at different wind speeds. At low wind speeds ($<1$ ms$^{-1}$) and high wind speeds ($>10$ ms$^{-1}$), the curves are close. They diverge by up to 5/6$^\circ$ for intermediate wind speeds, with the DFIR curve showing an increase with wind speed once the wind speed exceeds 4 ms$^{-1}$ and being relatively constant below that threshold. Under near-zero wind conditions, local turbulence induced by the instrument  should be minimal, making DFIR and unsheltered conditions comparable. One hypothesis could be that until 4 ms$^{-1}$ the DFIR is effective in minimizing local turbulence (DFIR curve constant, unsheltered curve abruptly increasing), while it gradually loses this capacity until "saturating" around 10 ms$^{-1}$ (DFIR curve increasing, unsheltered curve constant). This interpretation cannot unfortunately tell us any relevant information about the role of environmental turbulence, but only the likely effect of local turbulence introduced by the instrument.  Further research is therefore necessary to clarify these dynamics, in particular the role of natural turbulence in broadening the orientation distribution.

>>>>

Considering a population of hydrometeors rather than individual particles, as is often the case for practical applications, the distribution of orientations is often modeled with relatively narrow variability around 0$^\circ$ (i.e., horizontally oriented) values. Looking at the overview in Table~\ref{table:orientations}, one can observe that modeling studies mostly assume a Gaussian distribution, with standard deviations varying between 3$^\circ$ \cite{Matrosov_JAM_2001} and 60$^\circ$ \cite{Putnam_MWR_2017} depending on the type of hydrometeors. Observational studies conducted in the field \cite{Garrett_GRL_2015} confirm that differences exist due to hydrometeor type and environmental conditions (wind and turbulence). They report as well non-zero mean and median orientation values, which is contradictory with what was stated previously. As we will discuss later in this study, this discrepancy can be the result of the way multi-view instrumental observations are combined to retrieve an overall estimate of orientation, at least for more complex three-dimensional snow particles. A recent laboratory study using snow crystals replicas falling in an alcoholic solution~\cite{Stout_ACP_2024}, however, shows that in quiescent conditions individual planar crystals may have a spiralling fall regime with preferential orientations that depart from 0$^\circ$. A study with similar methods, but focussing on larger snow aggregates showed instead that horizontal orientation is preferred for those hydrometeors~\cite{Koebschall_EF_2023}. It is to be remarked that those and other studies, in considering objects falling in liquids, use a solid-to-fluid density ratio which is orders lower than in atmospheric precipitation. This may have far-reaching consequences in the settling dynamics~\cite{Tinklenberg_JFM_2023,Tinklenberg_JFM_2024}.

@@

Atmospheric conditions are expected to play a role in shaping orientation distributions: atmospheric turbulence is probably a key driver, as well as horizontal winds interacting with the instrument frame~\cite{Fitch_AMT_2021}. Turbulence has been shown to heavily impact the falling of particles in fluids in general~\cite{Petersen_JFM_2019,Brandt_ARFM_2022} and of frozen hydrometeors in particular~\cite{Nemes_JFM_2017,Li_JFM_2021}.

 Figure~\ref{fig:wind-effect} compares the standard deviation of orientation distributions between DFIR and unsheltered sites at different wind speeds. At low wind speeds ($<1$ ms$^{-1}$) and high wind speeds ($>10$ ms$^{-1}$), the curves are close. They diverge by up to 5/6$^\circ$ for intermediate wind speeds, with the DFIR curve showing an increase with wind speed once the wind speed exceeds 4 ms$^{-1}$ and being relatively constant below that threshold. Under near-zero wind conditions, local turbulence induced by the instrument  should be minimal, making DFIR and unsheltered conditions comparable. One hypothesis could be that until 4 ms$^{-1}$ the DFIR is effective in minimizing local turbulence (DFIR curve constant, unsheltered curve abruptly increasing), while it gradually loses this capacity until "saturating" around 10 ms$^{-1}$ (DFIR curve increasing, unsheltered curve constant). This interpretation cannot unfortunately tell us any relevant information about the role of environmental turbulence, but only the likely effect of local turbulence introduced by the instrument.  Further research is therefore necessary to clarify these dynamics, in particular the role of natural turbulence in broadening the orientation distribution.
